%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Personal Resume - Juan José Madrigal
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%% Packages

\documentclass[11pt]{article}
\usepackage[latin1]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[none]{hyphenat}
\hypersetup{colorlinks,urlcolor=light}
\usepackage{multicol}
\usepackage{array}
\usepackage{cancel}
\usepackage{color}
\usepackage{amssymb}
\usepackage{amsopn}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage[default,osfigures,scale=0.95]{opensans}
\setlength{\hoffset}{-2.85cm}
\setlength{\voffset}{-3.5cm}
\setlength{\textwidth}{525pt}
\setlength{\textheight}{730pt}
\setlength{\parindent}{0cm}
\definecolor{dark}{rgb}{0.15,0.30,0.4}
\definecolor{light}{rgb}{0.15,0.3,0.6}

%%%%%% Document

\begin{document}
	
\thispagestyle{empty} % No numbering

%%% Header

\begin{center}
{{\Huge\textsc{\color{dark}Juan José Madrigal Martínez}}}
\end{center}

\vspace{-0.4cm}

\textcolor{dark}{\rule{\textwidth}{3pt}}

%%% Personal data

\begin{minipage}[t]{7cm}
\flushleft
Madrid, Spain\\
(+0034) 600 86 32 48
\end{minipage}
\hfill
%%% Contact
\begin{minipage}[t]{7cm}
\flushright
juanjomadrigal326@gmail.com\\
	\href{https://es.linkedin.com/in/juan-jose-madrigal}{LinkedIn} \quad
	\href{https://github.com/jxm-math}{GitHub} \quad
	\href{https://www.kaggle.com/jxmmath}{Kaggle} \quad
	\href{https://profiles.udacity.com/u/juanjosmadrigal}{Udacity}
\end{minipage}

\vspace{0.4cm}

%%% Objective Statement

\textbf{Mathematician interested in Educational Technology, willing to explore new ways to bring advanced Mathematics to the world}. Especially gifted for

\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-2pt]
	\item Understanding and mastering Mathematics, interrelating all areas and branches
	\item Lecturing and teaching difficult or abstract concepts, both for beginners and experienced 
	\item Remarkable quick learning \\
\end{itemize}

%%% Skills

\vspace{-0.15cm}

{{\Large\textsc{\color{dark}Skills}}}

\vspace{-0.35cm}

\textcolor{dark}{\rule{\linewidth}{2pt}} \vspace{-0.7cm}

\begin{multicols}{2}
	\textbf{Programming Languages:} Python, Java, Android\\
	\textbf{Version Control Systems:} Git \& GitHub\\
	\textbf{Machine \& Deep Learning:} SciKitLearn, TensorFlow\\
	\textbf{Computer Vision:} OpenCV\\
	\textbf{Operating Systems:} Linux, Windows\\\\
	\textbf{Mathematics Softwares:} SageMath, Mathematica\\
	\textbf{Web Design:} HTML5 / CSS3 / JS, Angular4\\
	\textbf{Typesetting:} \LaTeX\\
	\textbf{Languages:} Native Spanish, Proficient English, German and French\\
\end{multicols}

%%% Projects

\vspace{-0.45cm}

{{\Large\textsc{\color{dark}Projects}}}

\vspace{-0.35cm}

\textcolor{dark}{\rule{\linewidth}{2pt}}\\ \vspace{-0.4cm}

\textbf{People Detector \& Tracker} \hfill Jun. 2017 

\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-2pt]
	\item Designed \textbf{CV-based detector} for people buying in a shop
	\item Successfully implemented \textbf{real-time tracker} counting entering and leaving people\\
\end{itemize}

\vspace{-0.2cm}

\textbf{Angular4 Front-End of WardenRetail App} \hfill Jul. 2017 

\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-2pt]
	\item Successfully integrated \textbf{\href{https://material.angular.io/}{Material Design}} and \textbf{\href{http://www.chartjs.org/}{ChartJS}} Components\\
\end{itemize}

%%% Experience

\vspace{-0.2cm}

{{\Large\textsc{\color{dark}Experience}}}

\vspace{-0.35cm}

\textcolor{dark}{\rule{\linewidth}{2pt}}\\ \vspace{-0.4cm}

\textbf{Artificial Intelligence Engineer} \hfill \href{http://wardenautomation.com/}{Warden Automation} $\vert$ Feb. 2017 - Present

\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-2pt]
	\item Designing \textbf{object recognition and tracking algorithms}\\
\end{itemize}

\vspace{-0.2cm}

\textbf{CEO of Mathifold Project} \qquad \href{http://mathifold.org/}{\texttt{http://mathifold.org/}} \hfill Madrid $\vert$ March 2014 - Present

\qquad[\textit{free, open-source online mathematics for students, teachers and workers}]

\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-2pt]
	\item Leading \textbf{15+ collaborators} including \textbf{mathematicians}, \textbf{computer scientists} and \textbf{engineers}
	\item Added \textbf{250+ posts} including \textbf{theory}, \textbf{exercises}, \textbf{animations} and \textbf{applets}, among other useful materials
	\item Recorded \textbf{800+ users} and \textbf{12000+ views} in the last 3 months\\
\end{itemize}

\vspace{-0.2cm}

\textbf{Lecturer \& Tutor at Faculty of Mathematics} \hfill UCM $\vert$ Sept. 2014 - Present

\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=-2pt]
	\item Lectured \textit{Intro to Mathematics}, \textit{Linear Algebra}, \textit{Real Analysis}, \textit{Probability \& Statistics}, \textit{Algebraic Topology}
	\item Taught and tutored \textbf{200+ students} both for \textbf{undergraduate and graduate courses}\\
\end{itemize}

%%% Education

\vspace{-0.2cm}

{{\Large\textsc{\color{dark}Education}}}

\vspace{-0.35cm}

\textcolor{dark}{\rule{\linewidth}{2pt}}\\ \vspace{-0.4cm}

\textbf{Udacity Deep Learning Nanodegree} \hfill Udacity $\vert$ Sept. 2017
	
\textbf{Udacity Machine Learning Nanodegree} \hfill Udacity $\vert$ Sept. 2016 - Feb. 2017

\textbf{Master in Advanced Mathematics} \qquad 9.81/10 - 3.75/4 \hfill UCM $\vert$ Sept. 2013 - Jul. 2014

\textbf{Degree in Mathematics} \qquad 9.92/10 - 3.87/4 \hfill UCM $\vert$ Sept. 2009 - Jul. 2013\\

%%% Awards

\vspace{-0.15cm}

{{\Large\textsc{\color{dark}Awards}}}

\vspace{-0.35cm}

\textcolor{dark}{\rule{\linewidth}{2pt}}\\ \vspace{-0.4cm}

\textbf{National Graduation Award} \hfill Sciences $\vert$ Spain

\textbf{Extraordinary End of Studies Award} \hfill UCM

\textbf{Honourable Mention} \hfill $\text{49}^{\text{th}}$ International Mathematics Olympiad, IMO $\vert$ Madrid $\vert$ 2008

\textbf{Gold Medal} \hfill $\text{44}^{\text{th}}$ Spanish Mathematics Olympiad $\vert$ Valencia, Spain $\vert$ 2008\\

\end{document}
